---
title: "Report: Fertility"
author: "YOUR NAME"
output: html_document
---

Here we've used the fertility data from the [gapminder web site](https://www.gapminder.org/data/) which contains the number of babies
born per woman accross countries in the world. The documentation for this data is available [here](https://www.gapminder.org/data/documentation/gd008/)
.

First we read in the data and process it, but you will need to make some changes to do the full analysis.

```{r raw_data}
fertility_raw <- readd(fertility_raw)

fertility_raw
``` 

We then pivot our data into long form and process our data

```{r fertility}
fertility <- readd(fertility)
fertility
```


# Line plot for all countries

```{r line-plot-all}
readd(line_plot_all)
```


# How has fertility changed in Australia?

```{r aus-line-plot}
oz <- readd(oz)

readd(line_plot_oz)
```


## Fit a linear model to Australia

```{r oz_mod}
mod <- readd(mod)
mod
```

## Plot the model fit against the data 

```{r oz_line_plot_mod_overlay}
readd(mod_plot)
```

## Summarise the fit

```{r mod-summary}
glance(mod)
```



